---
title: "Running DQD on Extension Tables"
author: "Maxim Moinat"
date: "`r Sys.Date()`"
output:
    pdf_document:
        number_sections: true
        toc: true
    html_document:
        number_sections: true
        toc: true
vignette: >
    %\VignetteIndexEntry{Running DQD on Extension Tables}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::knitr}
---

## Introduction
When you extend your OMOP CDM with custom tables and want to run DQD, then you need to extend the thresholds file.
A typical use case if you use the extension tables as proposed by the Imaging or Waveform Working Groups. 
With a few exceptions, the 20+ checks in the Data Quality Dashboard are generic and could be applied to extension tables.

However, the threshold file is not well suited for editing and maintenance in the current wide format.

The function `executeDqChecksOnExtension` solves this by taking long-format threshold files for the extension tables and fields, pivots them to wide-format, and then runs the DQD using those thresholds.
This allows users to maintain their threshold files in a more user-friendly format and run the DQD on their extensions without needing to modify the package source code.

## Usage
To use the `executeDqChecksOnExtension` function, you need to prepare long-format threshold files. Two examples below:

** Table level **

| cdmTableName | checkName                 | Threshold | Notes |
|--------------|---------------------------|-----------|-------|
| pregnancy    | cdmTable                |          |       |
| infant       | cdmTable                |          |       |
| pregnancy    | isRequired                |          |       |
| pregnancy    | measurePersonCompleteness | 100       |       |
| infant       | measurePersonCompleteness | 100       |       |

** Field level **

| cdmTableName | cdmFieldName                  | checkName               | Threshold | checkParameter     | checkParameter_TableName | checkParameter_FieldName | Notes |
|--------------|-------------------------------|-------------------------|-----------|--------------------|--------------------------|--------------------------|-------|
| pregnancy    | pregnancy_id                  | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | person_id                     | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_end_date            | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_id                  | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | person_id                     | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_end_date            | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | plausibleValueLow       | 1         | 19500101           |                          |                          |       |
| pregnancy    | pregnancy_start_date          | plausibleValueHigh      | 1         | DATEADD(dd,1,GETDATE()) |                   |                          |       |
| pregnancy    | gestational_length_in_day     | plausibleValueLow       | 1         | 0.0000001          |                          |                          |       |
| pregnancy    | gestational_length_in_day     | plausibleValueHigh      | 1         | 325                |                          |                          |       |

Then provide this table to the `executeDqChecksOnExtension` function as follows:
```{r eval=False}
DataQualityDashboard::executeDqChecksOnExtension(
  connectionDetails = connectionDetails,
  cdmDatabaseSchema = cdmDatabaseSchema,
  resultsDatabaseSchema = resultsDatabaseSchema,
  cdmSourceName = 'source_name',
  outputFolder = './',
  tableCheckThresholdExtensionLoc = "path/to/table_level_thresholds.csv",
  fieldCheckThresholdExtensionLoc = "path/to/field_level_thresholds.csv",
  conceptCheckThresholdExtensionLoc = "path/to/concept_level_thresholds.csv",
  ...
)
```

This will pivot the long-format threshold files to wide-format, run regular DQD using those thresholds, and return the results.
It will only execute the given checks.
So for a full QC, you will also need to run the regular `executeDqChecks` function with the default threshold files for the standard CDM tables and fields.

## Example

```{r eval=False}
myTable <- data.frame(id = c(1,2,3,4,5,6), person_id = c(1,NA,1,NA,1,99999))
tableLevel <- as.data.frame(
  rbind(
   c('tableName', 'checkName', 'threshold', 'notes')
  ,c('person','cdmTable',NA,NA) # Person is referenced in fieldLevel, so should be included here
  ,c('myTable','cdmTable',NA,NA)
  ,c('myTable','isRequired',NA,NA)
  ,c('myTable','measurePersonCompleteness',0,NA)
))
fieldLevel <- as.data.frame(rbind(
  c('tableName', 'fieldName', 'checkName', 'yTableName', 'yFieldName', 'threshold', 'notes')
  ,c('myTable','id','measureValueCompleteness','','',0,NA)
  ,c('myTable','person_id','measureValueCompleteness','','',5,NA)
  ,c('myTable','id','isRequired','','',5,NA)
  ,c('myTable','id','isPrimaryKey','','',5,NA)
  ,c('myTable','person_id','isForeignKey','person','person_id',5,NA)
))

tableLevelLoc <- tempfile(fileext = 'csv')
fieldLevelLoc <- tempfile(fileext = 'csv')
readr::write_csv(tableLevel, tableLevelLoc, col_names=FALSE)
readr::write_csv(fieldLevel, fieldLevelLoc, col_names=FALSE)

# dbPath <- tempfile(fileext = ".sqlite")
# con <- DBI::dbConnect(RSQLite::SQLite(), dbPath)
# on.exit(DBI::dbDisconnect(con), add = TRUE)

connectionDetailsEunomia <- Eunomia::getEunomiaConnectionDetails()
con <- DatabaseConnector::connect(connectionDetailsEunomia)

DBI::dbWriteTable(con, 'myTable', myTable)
DBI::dbGetQuery(con, 'select * from main.person;')

DBI::dbDisconnect(con)

results <- DataQualityDashboard::executeDqChecksOnExtension(
  connectionDetails = connectionDetailsEunomia,
  cdmDatabaseSchema = 'main',
  resultsDatabaseSchema = 'main',
  cdmSourceName = 'Eunomia+',
  outputFolder = tempdir(),
  tableCheckThresholdExtensionLoc = tableLevelLoc,
  fieldCheckThresholdExtensionLoc = fieldLevelLoc,
  checkLevel = c('TABLE', 'FIELD')
)
```


## Implementation notes
 - In contrast to the regular threshold files, you cannot specify in which schema each table can be found (CDM, VOCAB or COHORT).
   The function `executeDqChecksOnExtension` expects the tables are in the `cdmDatabaseSchema`.
 - The `cdmTable` and `cdmField` checks are implicit. The `cdmTable` check is made explicit by listing all tables with `cdmTable` check name, which makes sure that all tables are at least checked to exist. For field level thresholds, this is still implicit but it is expected that for all fields at least `measureValueCompleteness` is specified.
 - The processer checks if all tables in field-level are in table-level. And all fields in concept-level are in field-level file. If not, an error is thrown.

 - For testing, the default thresholds were transformed to the long format useing []`extras/thresholdWideToLong.R`](extras/thresholdWideToLong.R)