---
title: "Running DQD on Extension Tables"
author: "Maxim Moinat"
date: "`r Sys.Date()`"
output:
    pdf_document:
        number_sections: true
        toc: true
    html_document:
        number_sections: true
        toc: true
vignette: >
    %\VignetteIndexEntry{Running DQD on Extension Tables}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::knitr}
---

## Introduction
The checks in the Data Quality Dashboard are in principle generic and could be applied to any data model.
It is restricted to the OMOP CDM by the default given Threshold files.
To run the DQD on an extension, the user needs to provide the appropriate threshold files for the extension tables and fields. 
This has two issues:

1. This requires downloading the source code and build the package with a custom threshold file.
2. The threshold file, being a wide-format, is not well suited for editing and maintenance. An excel-like tool is needed to navigate the table and the wide table is very sparse.

To solve this, there is a new function `executeDqChecksOnExtension` that takes long-format threshold files for the extension tables and fields, pivots them to wide-format, and then runs the DQD using those thresholds. This allows users to maintain their threshold files in a more user-friendly format and run the DQD on their extensions without needing to modify the package source code.

## Usage
To use the `executeDqChecksOnExtension` function, you need to prepare long-format threshold files. Two examples:

** Table level **

| cdmTableName | checkName                 | Threshold | Notes |
|--------------|---------------------------|-----------|-------|
| pregnancy    | isRequired                | 0         |       |
| pregnancy    | measurePersonCompleteness | 100       |       |
| infant       | measurePersonCompleteness | 100       |       |
| pregnancy    | noAdditionalField         | 0         |       |
| infant       | noAdditionalField         | 0         |       |

** Field level **

| cdmTableName | cdmFieldName                  | checkName               | Threshold | checkParameter     | checkParameter_TableName | checkParameter_FieldName | Notes |
|--------------|-------------------------------|-------------------------|-----------|--------------------|--------------------------|--------------------------|-------|
| pregnancy    | pregnancy_id                  | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | person_id                     | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_end_date            | isRequired              | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_id                  | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | person_id                     | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_end_date            | measureValueCompleteness | 0         |                    |                          |                          |       |
| pregnancy    | pregnancy_start_date          | plausibleValueLow       | 1         | 19500101           |                          |                          |       |
| pregnancy    | pregnancy_start_date          | plausibleValueHigh      | 1         | DATEADD(dd,1,GETDATE()) |                   |                          |       |
| pregnancy    | gestational_length_in_day     | plausibleValueLow       | 1         | 0.0000001          |                          |                          |       |
| pregnancy    | gestational_length_in_day     | plausibleValueHigh      | 1         | 325                |                          |                          |       |

Then provide this table to the `executeDqChecksOnExtension` function as follows:
```{r eval=False}
DataQualityDashboard::executeDqChecksOnExtension(
  connectionDetails = connectionDetails,
  cdmDatabaseSchema = cdmDatabaseSchema,
  resultsDatabaseSchema = resultsDatabaseSchema,
  tableCheckThresholdExtensionLoc = "path/to/table_level_thresholds.csv",
  fieldCheckThresholdExtensionLoc = "path/to/field_level_thresholds.csv",
  conceptCheckThresholdExtensionLoc = "path/to/concept_level_thresholds.csv",
  numThreads = 1,
  sqlOnly = FALSE,
  sqlOnlyUnionCount = 1,
  sqlOnlyIncrementalInsert = FALSE
)
```

This will pivot the long-format threshold files to wide-format, run the DQD checks using those thresholds, and return the results. It will only execute the given checks. So for a full QC, you will also need to run the regular `executeDqChecks` function with the default threshold files for the standard CDM tables and fields. In the future we may add a parameter to run both the standard and extension checks in one go, but for now they need to be run separately.

## Example
```{r eval=False}
library(Eunomia)
library(DataQualityDashboard)
connectionDetailsEunomia <- Eunomia::getEunomiaConnectionDetails()
cdmDatabaseSchemaEunomia <- "main"
resultsDatabaseSchemaEunomia <- "main"

r <- DataQualityDashboard::executeDqChecksOnExtension(
  connectionDetails = connectionDetailsEunomia,
  cdmDatabaseSchema = cdmDatabaseSchemaEunomia,
  resultsDatabaseSchema = resultsDatabaseSchemaEunomia,
  cdmSourceName = "ExtensionExample",
  outputFolder = "output",
  tableCheckThresholdExtensionLoc = "extras/thresholdsLongFormat/long_OMOP_CDMv5.3_Table_Level.csv",
  fieldCheckThresholdExtensionLoc = "extras/thresholdsLongFormat/long_OMOP_CDMv5.3_Field_Level.csv",
  conceptCheckThresholdExtensionLoc = "extras/thresholdsLongFormat/long_OMOP_CDMv5.3_Concept_Level.csv",
  # checkLevel = c('TABLE'),
  checkLevel = c('TABLE', 'FIELD'),
  # checkLevel = c('TABLE', 'FIELD', 'CONCEPT'),
  writeToTable = FALSE
)

print(r)
```


## Implementation notes
 - In contrast to the regular threshold files, you cannot specify in which schema each table can be found (CDM, VOCAB or COHORT).
   The function `executeDqChecksOnExtension` expects the tables are in the `cdmDatabaseSchema`.
 - The `cdmTable` and `cdmField` checks were implicit, but made explict in long format threshold file. i.e. start of defining is listing all tables/fields with `cdmTable`/`cdmField` checks.
 - The processer checks if all tables in field-level are in table-level. And all fields in concept-level are in field-level file. If not, an error is thrown.
 - For field level thresholds, the expectation is that at least `measureValueCompleteness` is specified. The `cdmField` check is implicit.