---
params:
  results: null
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Data Quality Delta Report
This report summarizes changes in data quality across two executions of the data quality dashboard package.

### Metadata
TODO: add the dates for the two reports here

### Summaries
```{r echo=FALSE}
knitr::kable(params$results$overview, format="html") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed","responsive"))
```


### New Issues
The following issues were not present in the prior data quality execution but are now appearing as issues.
```{r echo=FALSE}
knitr::kable(params$results$newIssues, format="html") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Fixed Issues
The following issues were present in the prior data quality execution but are no longer issues.
```{r echo=FALSE}
knitr::kable(params$results$fixedIssues, format="html") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Arising Issues
The following checks are not failing, however the percentage of violating rows has increased since last execution.
```{r echo=FALSE}
knitr::kable(params$results$arisingIssues, format="html") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Improving Issues
The following checks are failing, however the percentage of violating rows has decreased since last execution.
```{r echo=FALSE}
knitr::kable(params$results$improvingIssues, format="html") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
